---
title: "R markdown tutorial"
author: "Mario Quaranta"
date: "Week 1"
output: pdf_document
---

This is a paragraph

# This is a section

## This is a subsection

### This is a subsubsection

This is an *italic* text, this is a **bold** text.

This is a list:

- Item one
- Item two
- ...
  - Sub item one
  - ...

This is a numbered list:

1. Item one
2. Item two
3. ...

# R code chunk

## Exercise 1

```{r}
# You can comment here
x <- seq(from = 0, to = 100, by = 2)
x
```

You can also write R code in test (called 'inline code'). This is the content of object x: `r x`.

## Plot

```{r, fig.width = 5, fig.width = 5, fig.align = "center"}
plot(x, x^2)
```

## Table

This is a table

-----------------------
Column 1 Column 2    
-------- --------------
1        1

1        1

1        1

1        1

1        1
-----------------------


See a tutorial [here](https://rmarkdown.rstudio.com/lesson-1.html)

See cheat sheet [here](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf)